---
title: "Reproducible Research - Peer Assessment 1"
output: html_document
---

**LOADING AND PREPROCESSING OF DATA**

1. Load the data

```{r}
if(!file.exists('activity.csv')){
    unzip('activity.zip')
}
activityData <- read.csv('activity.csv')
```

2. Process/transform the data (if necessary) into a format suitable for your analysis

```{r}
#activityData$interval <- strptime(gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", activityData$interval), format='%H:%M')
```

**WHAT IS MEAN TOTAL NUMBER OF STEPS TAKEN PER DAY**

```{r}
stepsByDay <- tapply(activityData$steps, activityData$date, sum, na.rm=TRUE)

```

1. Make a histogram of the total number of steps taken each day

```{r}

```

2. Calculate and report the mean and median total number of steps taken per day

```{r}
stepsByDayMean <- mean(stepsByDay)
stepsByDayMedian <- median(stepsByDay)

```
**WHAT IS THE AVERAGE DAILY ACTIVITY PATTERN?**

```{r}
averageStepsPerTimeBlock <- aggregate(x=list(meanSteps=activityData$steps), by=list(interval=activityData$interval), FUN=mean, na.rm=TRUE)

```
1. Make time series plot

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
mostSteps <- which.max(averageStepsPerTimeBlock$meanSteps)
timeMostSteps <-  gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", averageStepsPerTimeBlock[mostSteps,'interval'])

```

**Imputing missing values**

1. Calculate and report the total number of missing values in the dataset

```{r}
numMissingValues <- length(which(is.na(activityData$steps)))

```

2. Devise a strategy for filling in all of the missing values in the dataset.

```{r}


```

3. Create a new dataset that is equal to the original dataset but with the missing data filled in.

```{r}


```

4. Make a histogram of the total number of steps taken each day

```{r}


```

**Are there differences in activity patterns between weekdays and weekends?**

1. Create a new factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.

```{r}


```

2. Make a panel plot containing a time series plot

```{r}


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
